%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Template
% Version 1.0 (28/1/19)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended
%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.45\textwidth}
	\vspace{-\baselineskip}
	{\Huge\textbf{\MakeUppercase{Vladimir Mijić}}}
	
	\vspace{6pt}
	
	{\huge AI/ML Research Engineer}
\end{minipage}

\vspace{1cm}

\begin{minipage}[t]{0.3\textwidth}
    \vspace{-\baselineskip}
    
	{\faMapMarker \space}{Banja Luka, BiH}\\\\\\
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip}
	
	{\faEnvelopeO \space}{\href{mailto:vladocodes@gmail.com}{vladocodes@gmail.com}}\\\\
	%{\faEnvelopeO \space}{\href{mailto:vladomijic14@gmail.com}{vladomijic14@gmail.com}}\\
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip}
	
    {\faGithub \space}{\href{https://github.com/neuralmaticv}{GitHub}}\\\\
    {\faLinkedin \space}{\href{https://www.linkedin.com/in/vladimir-mijic}{LinkedIn}}
\end{minipage}

\vspace{0.1cm}



%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\colorbox{black}{{\textcolor{white}{\textbf{\MakeUppercase{Expirience}}}}}
\par\noindent\rule{\textwidth}{2px}\\

    {\textbf{AI/ML Research Engineer at LANACO}}\\
    {\faCalendarCheckO \space}{since October 2024}
    \begin{itemize}
        \item Engaged in research and development in the field of natural language processing, with a focus on applied AI techniques.
        \item Developed a computer vision-based parking occupancy detection system as part of LANACO’s smart city platform.
        \item Also developed a real-time edge computing solution for processing sensor data from industrial routers and LoRaWAN gateways.
        \item Mentored a group of 10 university students during an AI/ML internship programme centred on real-time data streaming. Delivered lectures, conducted hands-on workshops, and supervised end-to-end project development.
        \item \textbf{Tech stack}: Python, PyTorch, OpenCV, Hugging Face stack, MQTT, GStreamer, NVIDIA Jetson platform (JetPack, TensorRT, CUDA, DeepStream), Docker, Git\\
    \end{itemize}
    
    {\textbf{Scholarship Holder – AI/ML Research Student at LANACO}}\\
    {\faCalendarCheckO \space}{October 2022 -- October 2024}
    \begin{itemize}
        \item Worked on the development of a visual recommender system leveraging content-based image retrieval.
        \item Built a proof-of-concept automatic number plate recognition system using deep learning for detection and optical character recognition.
        \item Co-mentored a group of 15 university students during an AI/ML internship, delivering a technical workshop on retrieval-augmented generation using open-source LLMs.
        \item \textbf{Tech stack}: Python, PyTorch, TensorFlow, OpenCV, Hugging Face Transformers, Linux, Docker, Git\\
    \end{itemize}
    
    {\textbf{Embedded Software Intern at SYRMIA (now part of HTEC Group)}}\\
    {\faCalendarCheckO \space}{April 2024 \hfill \textit{(short-term university internship)}}
    \begin{itemize}
        \item Gained hands-on experience in embedded software development for the automotive industry.
        \item Contributed to system safety validation and build automation processes using CI pipelines and unit testing frameworks.
        \item Applied the Elastic Stack for system monitoring, data aggregation, and dashboard-based reporting.
        \item \textbf{Tech stack}: C, Elasticsearch, Logstash, Kibana, Git\\
    \end{itemize}

    
    
 %    {\textbf{JavaScript Developer - Museum of the Republic of Srpska}}\\
 %    {\faCalendarCheckO \space}{from May 2021 to May 2022, part-time}
	% \begin{itemize}
 %        \item Contributed to the development of interactive educational web-based games for children as part of the Museum of the Republic of Srpska exhibition project.
 %        \item Front-end and back-end development for quiz game 
 %        \item Tech stack: JavaScript, HTML and CSS \\
 %    \end{itemize}

    %{\textbf{Data Analyst Intern at m:tel company}}\\
    %{\faCalendarCheckO \space}{August 2021}
	%\begin{itemize}
	%    \item Introduction to Data Analytics, Data Warehousing, and Business Intelligence.
    %    \item  Tech stack: SQL, Python, Tableau and Power BI \\
    %\end{itemize}

\vspace{0.5cm}



%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\colorbox{black}{{\textcolor{white}{\textbf{\MakeUppercase{Education}}}}}
\par\noindent\rule{\textwidth}{2px}\\
        
    {\huge \textbf{BSc in Computer Science} \smallskip}\\
    \textbf{Faculty of Natural Sciences and Mathematics, University of Banja Luka}\\
    {\faCalendarCheckO \space}October 2020 -- Present \hfill \textit{Expected graduation: December 2025}
    
    \vspace{0.3cm}
    
	{\huge Telecommunication technician \smallskip}\\
    {\textbf{High School of Electrical Engineering "Nikola Tesla" Banja Luka}}\\
    {\faCalendarCheckO \space}{09/2016 - 05/2020}\\

\vspace{2cm}


%----------------------------------------------------------------------------------------
%	ADDITIONAL
%----------------------------------------------------------------------------------------

\colorbox{black}{{\textcolor{white}{\textbf{\MakeUppercase{Additional Professional Development and Achievements}}}}}
\par\noindent\rule{\textwidth}{2px}
\begin{itemize}
    \item Alumni and volunteer at the Bosnia and Herzegovina Futures Foundation
    \item Volunteer at the CODE4SEE Network (since 2023)
    \item Third place – Youth Innovation Award, Sarajevo, December 2023
    \item Volunteer – Data Science Conference Europe, Belgrade, November 2023
    \item Third place – Machine Learning Challenge at "barKod" Hackathon, Novi Sad, February 2023
    \item Associate member of the Association for Digital Transformation in BiH (2021–2022); initiated the Open Data BiH initiative.
\end{itemize}
\end{document}
